Infra-estrutura de Testes para Implementações de Referência do Standard ECMAScript

### 2022-05-11 paper.tex
escrever 2 paragrafo (ECMA standard many implementations so needs to have a "rigid" standard)

% Existem muitas implementacoes diferentes da linguagem: client-side (browsers), server-side (Node.js), embedded devices (Jerryscript) -> Estas implementacoes têm de estar de acordo no comportamento observavel -> é particularmente importante na Web -> senao temos sites que em ...
% -----------------------
% overview do standard -> descrita num standard
% Porque é muito importante que as várias implementacoes da linguagem coincidam -> o JavaScript está especificado num documento semi-formal que ...
% Falar sobre o standard
%   - o standard está como um interpretador de JavaScript em
%     pseudo-codigo - descreve detalhadamente os passos que
%    um interpretador de JS tem de executar ao avaliar qualquer
%    statement da linguagem
% Falar sobre o comité -  quem controla a evolucao do ECMAScript
ECMAScript standard is the official document in which the JavaScript language is defined. This document is in constant evolution, being updated by the ECMA Technical Committee 39 (TC39), which is responsible for maintaining the standard. The standard is currently in its twelfth version.
%
JavaScript is specified in the ECMAScript standard\cite{ECMAScriptStandard}, which is written in English, and subsequently implemented by various  compilers and interpreters. Some of the JavaScript compilers are the ~\cite{Hop} and the JSC~\cite{JSC} compilers.
Most popular interpreters being nodejs~\cite{nodejs} and spidermonkey~\cite{spidermonkey}.
%
The standard defines the types, values, objects, properties, syntax, and semantics of JavaScript that must be the same in every JavaScript compiler and interpreter, while allowing JavaScript implementations to define additional types, values, object, properties, and functions.

>>>>

% Existem muitas implementacoes diferentes da linguagem: client-side (browsers), server-side (Node.js), embedded devices (Jerryscript) -> Estas implementacoes têm de estar de acordo no comportamento observavel -> é particularmente importante na Web -> senao temos sites que em ...
% -----------------------
% overview do standard -> descrita num standard
% Porque é muito importante que as várias implementacoes da linguagem coincidam -> o JavaScript está especificado num documento semi-formal que ...
% Falar sobre o standard
%   - o standard está como um interpretador de JavaScript em
%     pseudo-codigo - descreve detalhadamente os passos que
%    um interpretador de JS tem de executar ao avaliar qualquer
%    statement da linguagem
% Falar sobre o comité -  quem controla a evolucao do ECMAScript
ECMAScript standard\cite{ECMAScriptStandard} is the official document in which the JavaScript language is defined. This document is in constant evolution, being updated by the ECMA Technical Committee 39 (TC39), which is responsible for maintaining the standard. The standard is currently in its twelfth version.
%
JavaScript is specified in the ECMAScript standard using the English language. Subsequently, the standard is implemented by various  compilers and interpreters. Some of the JavaScript compilers are the ~\cite{Hop} and the JSC~\cite{JSC} compilers. Most popular interpreters being nodejs~\cite{nodejs} and spidermonkey~\cite{spidermonkey}. These are only four implementations amongst many others, which come along with the many use cases that JavaScript has. JavaScript is used mostly used in the web context, both client-side within browsers and server-side \texttt{(Node.js)}, but also in embedded devices.
%
Since JavaScript is used in so many scenarios and across so many different contexts, there is a great need for the ECMAScript standard to define in grate detail to ensure consistency. Browsers, for example, need to run JavaScript implementations that coincide so that websites are correctly rendered. In order to achieve coherent implementations, the standard defines the types, values, objects, properties, syntax, and semantics of JavaScript that must be the same in every JavaScript compiler and interpreter, while allowing JavaScript implementations to define additional types, values, object, properties, and functions.
